### 2013-05-21 Publications/2013-TMI/04-methods.tex
Fixed some minor mathematical details
Section II.A

\section{Methods}
\label{sec:methods}
%
\subsection{Maximum A-Posteriori Model}
\label{sec:methods_map}
%
A widely used approach to image segmentation is derived from the
Bayes' rule (\autoref{eq:bayes_rule}), where one seeks for a partitioning
of a certain image $X$ in piecewise smooth regions $\Omega_k$, 
with $k \in \lbrace 1 .. K \rbrace$, that maximizes the a posteriori 
probability given the multivariate image $X \in \mathbb{R}^C$, 
with $C$ being the number of image channels.
\begin{equation}
p(Y \mid X) = \frac{p(X \mid Y)\, p(Y)}{p(X)}.
\label{eq:bayes_rule}
\end{equation}

Therefore, $Y$ is a certain realization of the piecewise 
disjoint region set $\Omega_k$. $p(X \mid Y)$ is the \emph{likelihood} of 
the realization of $X$ (the image) given a certain distribution model for 
each region $k$. The second term, $p(Y)$, is the a-priori probability of 
the partitioning $Y$. Finally, $p(X)$ is the probability of a certain image 
realization, and thus, it will remain constant when computing the \gls{map}.
Consequently, $p(Y \mid X) \propto p(X \mid Y)\, p(Y)$, and:
\begin{equation}
\textrm{argmax} \left\{ p(Y \mid X) \right\} = 
\textrm{argmax} \left\{ p(X \mid Y)\, p(Y) \right\}.
\end{equation}

>>>>

\section{Methods}
\label{sec:methods}
%
\subsection{Maximum A-Posteriori Model}
\label{sec:methods_map}
%
A widely used approach to image segmentation is derived from the
Bayes' rule (\autoref{eq:bayes_rule}), where one seeks for a partitioning
of a certain image $X$ in piecewise smooth regions $\Omega = \lbrace \Omega_k , 
k\in\left[ 1 .. K \right] \rbrace$,  that maximizes the a posteriori 
probability given the multivariate image $X \in \mathbb{R}^C$, 
with $C$ being the number of image channels.
\begin{equation}
p(Y \mid X) = \frac{p(X \mid Y)\, p(Y)}{p(X)}.
\label{eq:bayes_rule}
\end{equation}

Therefore, $Y$ is a certain realization of the piecewise 
disjoint region set $\Omega$. $p(X \mid Y)$ is the \emph{likelihood} of 
the realization of $X$ (the image) given a certain distribution model for 
each region $\Omega_k$. The second term, $p(Y)$, is the a-priori probability of 
the partitioning $Y$. Finally, $p(X)$ is the probability of a certain image 
realization, and thus, it will remain constant when computing the \gls{map}.
Consequently, $p(Y \mid X) \propto p(X \mid Y)\, p(Y)$, and:
\begin{equation}
\textrm{argmax} \left\{ p(Y \mid X) \right\} = 
\textrm{argmax} \left\{ p(X \mid Y)\, p(Y) \right\}.
\end{equation}
